A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-10 faculty.tex

\section{Collaboration and co-authorship}
While it's general true that profs. are busy, but for me and probably many others, it's not the main reason.  I do skim every single emails from prospective students, but I ignore most of them because they were quite generic (likely written for dozen of other profs.).  Sometimes they try to "customize" it by mentioning the names of my papers, but

.  So even if I am not busy (e.g., spending time on reddit), I still would not reply to such emails.

>>>>

\section{Collaboration and co-authorship}
While it's general true that profs. are busy, but for me and probably many others, it's not the main reason.  I do skim every single emails from prospective students, but I ignore most of them because they were quite generic (likely written for dozen of other profs.).  Sometimes they try to "customize" it by mentioning the names of my papers, but the contents are still quite irrelevant.  So even if I am not busy (e.g.,  spending time on reddit), I still would not reply to such emails.

For the OP: you can follow up with an email now since it has been almost a month,  or do it later.  I wouldn't care if you send now or later --  if it's generic I'll ignore it,  but if it is personalized and especially relevant to my work, I'll likely reply.  If I am not, then you can assume I am not the right fit and should move on.
